\documentclass[]{iac}

\DeclareMathOperator{\E}{E}
\DeclareMathOperator{\prob}{p}
\DeclareMathOperator{\tr}{tr}

\newcommand{\etalia}{\textit{et al.}}
\newcommand*{\vectornorm}[1]{\left\|#1\right\|}
\newcommand*\rfrac[2]{{{}^{#1}\!/_{#2}}} % running fraction with slash - requires math mode.
\newcommand*\T{\mathsf{T}}

\begin{document}

\IACpaperyear{17}
\IACpapernumber{D9.2.8}
\IACconference{65}
\IAClocation{Toronto, Canada}
\IACcopyrightA{2014}{the authors}

\title{Technology demonstrator of a rocket carrying a deployable fleet of autonomous gliders}

%\author{Main~Author\\Affiliation, Country, email address\and
%		Co-Author\\Affiliation, Country, email address}
\IACauthor{Patrick Spieler}{Swiss Federal Institute of Technology, Lausanne, Switzerland, }
\IACauthor{Co-Author}{Affiliation, Country, email address}

\abstract{%Rewrite: Dalmir, Sorina
%NOTE: Many of the structure of paper goes to the end of introduction
%The Intercollegiate Rocket Competition (IREC) aims to gather students from across the world to design and build a rocket that reaches an altitude of 3km or 10km, carrying a 4kg of payload. As part of this competition, the Team Duster, formed by students from Swiss universities developed a rocket with a payload targeting an apogee of 3km. \\ 
%Firstly, the rocket flying to 3km will be presented, along with its design and manufacturing processes. The rocket then follows a dual-event recovery process. Firstly, the drogue (small) parachute is deployed, reducing the speed of the rocket to about 30 m/s. At the same time the separation of the nosecone occurs thereby releasing the payload. After the rocket descends to an altitude of 457 meters, the second (main) parachute is deployed, reducing the speed to 6m/s. Throughout the launch, separation, and landing phases, we constantly received telemetry (information) provided by the custom-designed avionic components placed in the nosecone of the rocket. To ensure that the deployment occurs at predefined altitudes, the decision was made to use 2 redundant systems for altitude measurement -independent of the avionics placed in the recovery bay. The trajectory of the rocket was simulated in 3 varying environments, including our own developed simulator. The rocket made its first flight towards the end of March 2017 in Switzerland where its flight data was compared with the simulation data. Based on this data, the necessary trajectory corrections were performed in order to improve the competition Flight - which occured in mid-June. \\
%Secondly, an innovative payload that flew in the rocket will also be presented. A fleet of 3 gliders are deployed from the rocket at apogee using a release based on a spring mechanism. Equipped with an autopilot, differential GPS, and control surfaces using servomotors, the gliders autonomously fly in formation. Eventually, they land at a fixed point on the ground. The gliders have. During the flight, the gliders transmit information back to the groundstation and are tracked using custom-made ground station.  Potential video-recording of the flight will be investigated in the future.
%The results of the intermediary flight (end-of-March) as well as the competition flight - both in terms of rocket trajectory and flight of the gliders - is included in the paper, along with further recommendations for a more advanced technology demonstration in the future.

The Intercollegiate Rocket Competition (IREC) aims to gather students from across the world to design and build a rocket that reaches an altitude of 3km or 10km, carrying a arbitrary payload of 4kg. As a part of this competition, team Duster, formed by students from 3 Swiss universities developed and constructed a rocket with a payload targeting an apogee of 3km. The rocket is launched by using COTS solid motor. It follows a a dual-event recovery process with first parachute deployment at apogee and second (main) parachute deployment at 457 meters.  Custom avionics inside the nosecone log and transmit information back to the ground.
Inside the rocket a payload of 4 kg is placed and that payload consists of a custom built autonomous glider ejected at apogee, which descends to a fixed point on the ground independent from the rocket. 
To estimate the apogee under variety of conditions and motor configurations 3 separate simulators are used with one being developed by the team as a part of this project. Especially interesting in this context is also the stability - both static and dynamic, which influences the design and has large impact on the performance of the rocket. 
The technology behind both the rocket and the payload together with concepts for autonomous fleet of gliders is presented and elaborated on in this paper. Design process and manufacturing, together with tests done and issues faced over the course of the project are also presented along with the solutions and recommendations for the future.
}

\maketitle
%Check for number of pages allowed, if any
\section{Introduction}

%Spaceport America Cup (formerly entitled Intercollegiate Rocket Competition (IREC)) gatheres students all over the world to participate at the biggest rocket challenge. Students are launching solid, liquid, and hybrid rockets to target altitudes of 10,000 feet (3048 meters) and 30,000 feet (9144 meters), carrying 8,8lb (3.9 kg) of payload.

%Team DUSTER, representing several Swiss universities, entered this contest to build a solid motor rocket flying to an apogee of 10,000 ft (3048 meters). The project received an honourable place 8$^th$, out of 83 teams.

%This paper contains the work developed by the team of students between November 2016 and June 2017. The first part of the article discusses the rocket design, manufacturing and flight data. The second part of the article reviews the payload placed inside the rocket. For this year, the team built a glider that was deployed at 10,000 ft and flew back to the ground. For the future, the aim is to develop a fleet of gliders that is deployed from the rocket at apogee and flies in formation back to the ground. As part of this article, the fleet of gliders will be only conceptually discussed.
Spaceport America Cup (formerly entitled Intercollegiate Rocket Competition (IREC)) gathers students from all over the world to participate at one of the biggest rocket competition. Students are launching solid, liquid, and hybrid rockets to target altitudes of 10,000 feet (3048 meters) and 30,000 feet (9144 meters), carrying 8,8lb (3.9 kg) of payload. The teams are scored according to the flight performance on the competition day, technical implementation, the quality of the report and research done as a part of the project.
Team DUSTER, representing several Swiss universities, entered this contest to build a solid motor rocket flying to an apogee of 10,000 ft (3048 meters). 
The main objective of the rocket is to achieve an apogee of 10,000 ft exactly. Deviations from this apogee result in point loss in the flight performance category. At the apogee, 2 separation events occur: separation alongside the body of the rocket where the parachutes are ejected and separation of the nosecone form the rocket. 
Recovery subsystem is responsible for obtaining this precise apogee and ensure the deployment of the parachutes. This system consists of 2 parachutes and 2 redundant instruments which are used to estimate the apogee and trigger the separation of the rocket. After the separation occurs, both parachutes are ejected from the body of the rocket and one is opened , the so-called drogue, reducing the speed of the rocket to about 30 m/s. The main parachute remains in the bag for the first part of the descend. At the same time the nosecone is also separated from the rocket and the glider is ejected. From this point the rocket consisting of 3 parts (2 body parts and the nosecone) and the glider descend independently from each other. At the altitude of 457 meters, the second (main) parachute opens, reducing the speed to 6m/s. Throughout the launch, separation and landing phases telemetry information, provided by the custom-designed avionic components placed in the nosecone of the rocket, are being constantly logged and part of them also sent to the ground station. 
In the model flown at this years competition no control mechanism were in place and also no air brakes were installed meaning once the rocket is launched the trajectory can not be influenced. This increased the importance of simulation, as the only way to determine the altitude the rocket can obtain with a chosen motor and assuming certain weather conditions.  The trajectory of the rocket was simulated in 3 varying environments, including our own developed simulator. 
The second main component of the project is the payload. The payload is an autonomous glider equipped with an autopilot, differential GPS, and control surfaces using servomotors. Its objective is to land at a fixed point on the ground and transmit data from the sensors to the ground station. In this years model only one glider had been constructed with a wing span of approximately 200mm and a body length of 100mm. The concept of multiple gliders flying in a formation is presented as well with a possibility of being implemented in next years model.  
The results of the intermediary flight (end-of-March) as well as the competition flight - both in terms of rocket trajectory and flight of the gliders - is included in the paper, along with further recommendations for a more advanced technology demonstration in the future

The structure of this paper is as follows: in the first section the rocket is presented together with 4 main subsystems: structure, avionics, propulsion and recovery. Section 2 covers the design and technology used in a glider and presents a concept of a fleet of gliders. Navigation and control, one of the main challenges in glider design, are elaborated in detail in Section XX. The last part contains the conclusion and the outlook for the future. 




\section{Rocket}




\input{rocket}


\section{Gliders}

\subsection{General Overview}

\subsection{Design and Manufacturing of ONE glider-SORINA}
%Pictures from report here

\subsection{Design and Manufacturing of a fleet of gliders-SORINA}
%Concept TBD in solidworks 

\subsection{Navigation and Control of the fleet of gliders}
%Ultrawide beacons 
%Formation
%Check for alternative options, instead of GPS


\section{Conclusions}
\section{Outlook}
%Maybe talk about airbrakes, active control, etc.

\end{document}